\documentstyle [11pt]{article}
\textwidth 5.5in
\textheight 10in
\topmargin -.60in
%%%\oddsidemargin 0.0in
\begin{document}
\pagestyle{empty}
\begin{center} {\LARGE Daniel A. Oblinger}\\
\vspace{1mm}
\small
Department of Computer Science\\ 
2036 Neil Drive\\
Columbus, Ohio 43210\\
(614) 293-0740~~~~~~~~~~(606) 586-7896
\end{center}
\vspace{0mm}

\begin{enumerate}
\leftmargin 6in
\listparindent 0in

%%%%%%%%%%    \item [ {\protect\makebox[1.2in][l]{ \bf OBJECTIVES}} ] 
%%%%%%%%%%	Software development engineer.  Software architect.

    \item [ {\protect\makebox[1.2in][l]{\bf EDUCATION}}] 
	Second year graduate student in
	Computer Science at Ohio State University, GPA 4.0.  Obtained a
	B.S. in Computer Science and Mathematics from Northern Kentucky 
	University, May 1987.  Graduated {\em Suma Cum Laude}\/ with 
	{ 3.92}/4.0 overall and a { 4.0}/4.0 in both majors.\\
	{{\em Programming languages/environments:}
        VMS, UNIX, MS-DOS,
	Pascal, C, Fortran, Basic, LISP, Smalltalk, Modula II,
	and many assemblers.}
	
    \item [{\protect\makebox[1.2in][l]{\bf EXPERIENCE}}]

    \item [{\protect\makebox[1.1in][l]{9/87 to present}}]
	{\sl Ohio State University.} Graduate Teaching Associate.
	Developed curriculum and taught CIS 459 - LISP, which was new
	to OSU's curriculum.
	Responsible for all lecturing and grading 
	for  CIS 221 - Pascal for engineering majors (20 hrs/wk).

    \item [{\protect\makebox[1.1in][l]{6/88 to 9/88}}]
	{\sl IBM.} San Jose, CA.
	Software Engineer.  Designed and implemented task synchronization
	primitives which are to be used as the building blocks for 
	more than five languages on the IBM 370.  Composed
	users manual and document justifying the implementation's efficiency, 
	and correctness on a multiprocessor system (Full time).

    \item [{\protect\makebox[1.1in][l]{3/88 to 5/88}}]
	{\sl Ohio State University.} Research Associate.  Developed the
	semantics, designed,
	and implemented a data-directed control flow mechanism 
	used to drive part of the AI toolset, upon which many
	AI applications have been written (20 hrs/wk).

    \item [{\protect\makebox[1.1in][l]{7/85 to 8/87}}]
	{\sl Midwest Communication Corporation.} Edgewood, KY. 
	Computer operator (30 hrs/wk).

    \item [{\protect\makebox[1.1in][l]{12/84 to 8/86}}]
	{\sl Doug Ragland.}  Lexington, KY. 
	Software Engineer.  Sole Designer and implementor of a programming and
	text processing environment for the handicapped (still in use).
	Environment
	included an extensive programmable editor, note retrieval facility,
	and auto word completion dictionary.  System designed to 
	minimize keystrokes.

    \item [{\protect\makebox[1.1in][l]{5/84 to 8/84}}]
	{\sl Northern Kentucky University.}
	Attendant for a mute quadriplegic.    
	Physically assisted quadriplegic in all functions (Full time).

    \item [{\protect\makebox[1.1in][l]{1/84 to 6/85}}]
	{\sl Northern Kentucky University}.  Tutor for
	Calculus, Fortran, and Pascal (15 hrs/wk).

    \item [{\protect\parbox[t]{1.2in}{\bf HONORS \&}}]
	ACM Regional Programming Contest. Participated on O.S.U.'s 
	team (6$^{th}$ place) 
\vspace{-11pt} 
       \item [{\protect\parbox[t]{1.2in}{\bf ACTIVITIES}}]
	and N.K.U.'s team (7$^{th}$ place).
	A.H.P. {\em Mathematics} competition. 
	Placed {\sl second} as a Freshman and {\sl first}
	as Sophomore.
	Dean's Scholarship Junior \& Senior years.
	ACM Member (4 Years). 
        IEEE Member (1 Year).
	Intramural volleyball (3 Years).

    \item [{\protect\makebox[1.2in][l]{\bf INTERESTS}}]
	A.I. based {\sl home automation},
	Camping/Hiking,
	Racquetball, and 
	Water Skiing.


%%%    \item [{\protect\makebox[1.5in][l]{\bf REFERENCES}}]
%%%	Available on request.

\end{enumerate}  

\end{document}
