\documentstyle[12pt]{article}
\begin{document}
\vspace{-10mm}
\begin{center}\LARGE{SUPPLEMENT}\end{center}
\begin{center}\large{Daniel Anthony Oblinger\\ 401-11-1846}\end{center}
\vspace{10mm}
{\Large\bf SCHOLARSHIPS}
\begin{itemize}

	\item RA/TA at The Ohio State University (2 Years).
	\item Dean's Scholarship Junior and Senior Years.
	\item Departmental Scholarship (3 Years).

\end{itemize}
\vspace{10mm}
{\Large\bf ACCOMPLISHMENTS}
\begin{itemize}

	\item Developed the semantics, designed and implemented a data-directed
	control flow mechanism as a research associate at OSU.  The mechanism 
	drives part of the AI toolset upon which many AI applications have
	been written.

	\item Designed and implemented a 
	{\em frame based object oriented language for home automation}.
	HAL (Home Automation Language) uses a message sending mechanism
	which is a generalization of Smalltalk's message send.
	All knowledge in the system is embedded
	in a virtual frame database derived from Minsky's frames.  The 
	constructs of the language are defined using a restricted 
	form of attribute grammars (for efficiency).  Even these 
	attribute grammars are contained within the database to allow easy
	extension/modification of the language.
	I have been designing/redesigning this language for over 4 years.
	On top of this language I have built programs which utilize a speech
	synthesizer, A to D converter, touch-tone phone decoder, and many
	TTL \& relay lines.  All of which I have built and added to my
	PC-AT.

	\item Designed and implemented task synchronization primitives 
	as a software engineer for IBM.  Primitives are to be used for
	more than five languages on the IBM 370.

	\item Composed a document to be used as part of a users manual
	for the above synchronization primitives.  Also wrote a second
	document which contains an informal proof that the primitives
	perform according to specification in a multitasking/multiprocessor
	environment. 

	\item Drafted proposal for, designed, implemented, and tested a text
	processing environment for the handicapped which is still in use.
	Environment included an extensive programmable full screen editor,
	a note-indexing facility, and an automatic dictionary
	which interactively completes word being typed.  
	System is designed to minimize keystrokes.

	\item Implemented {\em XINU}, a multi-tasking networking operating
	system written on a bare IBM-PC.

	\item Designed and implemented a dialect of {\em LISP} for
	6809 based personal computers.  The interpreter uses a shallow
	binding scheme and has fifty-five primitives most of which are
	list manipulation or control flow primitives including:
	CATCH/THROW/UNWINDPROTECT, error trapping, and a non-local
	GO that can change the context in effect.

	\item Implemented a recursive-descent compiler for a 
	statically-scoped language similar to PASCAL.

	\item Research Paper (unpub) ``Knowledge Representations Used In 
	Learning.''

	\item Worked with faculty to expand undergraduate Computer Science 
	Curriculum to include a class on Automata Theory and Formal Languages.

\end{itemize}
\vspace{10mm}
{\Large\bf AWARDS AND ACTIVITIES}
\begin{itemize}

	\item Graduated Suma Cum Laude.
	\item Outstanding Student of the Year Award in both Mathematics
	and Computer Science.
	\item 4.0 in Mathematics, 4.0 in Computer Science, 3.92
	in Undergraduate, 4.0 in Graduate.
	\item AHP Mathematics Competition, first and second place.
	\item ACM Regional Programming Contest, sixth place with OSU's 
	team and seventh place with NKU's team.
	\item President of undergraduate computer science club.
	\item Listed in Who's Who's in both High School and College.
	\item Member of ACM (3 Years).

\end{itemize}
\vspace{10mm}
{\Large\bf TEACHING EXPERIENCE}
\begin{itemize}

	\item Developed and taught CIS 459 - LISP, a course which was new
	to OSU's Computer Science curriculum.

	\item Instructor for a special Pascal course taught through
	Ohio State at Bell Laboratories.
	\item Recitation instruction for a Pascal class at Ohio State.

	\item Tutor and assistant in all functions for a mute quadriplegic.
	Tutored Pre-Calculus, Calculus I, Calculus II, Pascal, and Fortran.
	(Physical assistant during the Summertime only.)

\end{itemize}
\end{document}

