\documentclass[10pt]{letter}
\usepackage{beckman}
\newcommand{\comment}[1]{}
\newcommand{\nocomment}[1]{#1}


% New OBJECTIVE
% "Expert knowlege of..."
% New activities in activities section
% Check dates on NKU scholarships
% Check all dashes
% ADD Professional organizations
% Get location of AIPS
% 
% Marsha:
% 	Place for TJ watson.  None of the others have place.
% 	Periods at end of phrase entries?
% 
% 
% Info per Company:
% - Company name
% - Person name
% - Company address
% - Datamining connection
% - Other connecting sentences

% I have a broad technical background ranging from theoretical to
% low-level including a bachelors in
% Mathematics with a focus in formal mathematics (algebra, real
% analysis, complexity theory, combinatorics, etc.).  I have implemented a 
% number of fairly large applications: my thesis; a handicap's
% programming/editing environment; an extensive LISP interpreter; a
% simple UNIX-like multiprocessing operating system for the 80286
% processor; a native code, optimizing compiler for a PASCAL-like
% language; and an accounting/organization package for a soccer league.
% I also have low-level coding and hardware experience that includes
% many digital and analog circuits, assembly language programming (video
% processing, games, LISP interpreter, etc.), and use of low-level APIs 
% (X-windows, DOS, UNIX, etc.).


\comment {

Intro
+  Ph.D. in artificial intelligence from University of Illinois.
+  interested in full-time employment for fall of 1997

Credentials
+  "Plausible Inference: An knowledge-intensive, inductive approach to
    domain modelling"
-  Approach to machine learning that uses rules (written) to 
-  Applied learning model to the grand challenge prob. of prot. str. prediction
-  Learning model is implemented in parallel on a 512 node CM5 supercomputer.
X  15,000 lines of C and LISP.
- appropriate for tough domains w. knoweldge

> Technical: (broad technical background)
- BS in Mathematics
- Fairly large applications: handicap, thesis editor/programming env.
- Low-level applications including: many digital and analog circuts, 
  x-windows, DOS, UNIX

> Interpersonal: Teaching/presentation. T.J. Watson

> My career objective
  - long been to do research in machine learning.
  - Through working at T.J. Watson and as a consultant on protein
  str. prediction I found my enthusiam and ability also lie in
  (1) working as a specialist within a larger group, and
  (2) synthesizing elegant, practical interfaces and designs for
  large software systems.

  Thus the ideal position would involve the research issues surrounding
  a concrete data mining application or product.  It would require me
  to provide expertise in machine 
  learning within a larger team.  This job would have the
  potential for publication, and the potential for growth toward
  technical management/software architect type position.

  A position with XXX-company provides many of these opportunities.
  ...

  


[RESEARCH|DEVELOPMENT], DATA-MINING, [CONSULTANT], [PROTEIN]



Fit  (Number of things makes good match) 
-  My consulting experience in bio is similar to the role of data mining
   consultant:
-  For two years I worked closely with a group of biologists encoding
   expertise foreign to myself into a framework foreign to them.
-  Enjoyed/excelled at: selling model \& arriving at common understanding.


Communicate Skills:  
   Technical, Designing, Programming, 
   Interpersonal: presentation(selling), communication, writing, management
   Eager/hard-working
}

\comment{ UNUSED STUFF


\begin{tabbing}
\hspace*{5in}\=\kill\\
\>Daniel Oblinger\\
% \>Beckman Institute\\
% \>University of Illinois\\
\>405 N. Mathews\\
\>Urbana, IL 61801\\
\>April 25, 1997
\end{tabbing}

XXX Company \\
XXX Street \\
XXX City, State \\
\vspace{.25in}

Dear XXXX recruiting,



\begin{tabbing}
\hspace*{5in}\=\kill\\
\vspace*{.5in}
\>Sincerely,\\
\vspace*{.75in}
\>Daniel A. Oblinger\\
\end{tabbing}

}


% \pagenumbering{none}
% Regular page size
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}  % was 9
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.2in}
\setlength{\itemindent}{.25in}

\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\topskip}{0.0in}
% \setlength{\footheight}{0.0in}
\setlength{\footskip}{0.5in}

% YAP sized pages
% \pagestyle{empty}
% \setlength{\topmargin}{-1.5in}  % .95
% \setlength{\textwidth}{5.5in}
% \setlength{\textheight}{3.7in}
% \setlength{\oddsidemargin}{-0.95in}
% \setlength{\evensidemargin}{-0.95in}

% Personal Information
\telephone{(217) 244-1503}
\email{oblinger@uiuc.edu}
\signature{Daniel A. Oblinger}


\begin{document}
\begin{letter}
 {XXX-street\\
  XXX-city-state\\
  April 19, 1997\\}

\opening{Dear XXXX Recruiter,}

I will be graduating in October 1997 with a Ph.D. in Computer Science
(Artificial Intelligence) from the University of Illinois at Urbana
Champaign.  I am interested in employment at XXX, and will available
for full-time employment immediately after graduation.  I anticipate
making an employment decision before July 15.

\par

Through my graduate studies I have gained considerable experience in
data mining and its application to important/practical learning tasks.
%
My dissertation, ``Plausible Inference: A knowledge-intensive approach
to domain modeling,''  was carried out under the direction of Gerald
DeJong.
%
Plausible Inference (PI) is an inductive learning framework that
relies on several forms of structured knowledge we found to be
commonly available sources of domain expertise.
%
PI employs this domain expertise as a strong, problem-specific
bias through which it induces predictive models of
complex domains.
%
In my research, I applied PI to a difficult biological task--protein
structure prediction--by 
implementing a parallel version of PI in a combination
of C and LISP which ran on a CM5 supercomputer.
%
My dissertation serves as a strong foundation for further work
bridging reseach and development, particularly in the application of
learning/mining techniques to other areas.

\par

In additional to the technical positions I have held, I have fulfilled
a variety of roles in both academic and professional
settings.  Most recently I served as an AI consultant to a biologists
research group.  
%
We encoded their intuitions as testable,
computational models of protein folding.
%
Also, while at the University of Illinois, I collaborated with a
number of professors on various publications and successful grant proposals.
%
At IBM T.J. Watson Research Center, I worked with a second-line
manager on the design of an expert system shell; part of my duties
included presentations of initial versions of this design to managers
of groups that would implement the shell.
%
At Ohio State University I enjoyed teaching several university-level
courses (one of which I designed).  The body experience I have
accumulated affords me the written, oral, interpersonal,
and organizational skills essential for continued personal growth and
far-reaching contributions at XXX.

\par

My career objective has long been to work in AI reseach
and development.  Through the experiences outlined above, I have
determined that my enthusiam and
ability also lie in (1) working as a specialist within a larger group,
and (2) synthesizing elegant, practical interfaces and designs for
large software systems.
%
Thus, the ideal position for me would involve both the research and
development on concrete data-mining/machine learning
application.  It would involve close collaboration with professional
in other fields or other companies.  This position would also 
permit me to publish my research, and have the potential for continued
professional growth, perhaps culminating in a technical
management/software architech role.

\par

A position with XXX-company affords many of these opportunities.
Your work on ...

\par

Thank you for your time and consideration.  Please do not hesitate to
contact me for references from my recent collaborations or if you have
any other questions.

\closing{Sincerely,}

\end{letter}

\end{document}
