\documentclass[10pt]{letter}
\usepackage{beckman}
\newcommand{\comment}[1]{}
\newcommand{\nocomment}[1]{#1}


% New OBJECTIVE
% "Expert knowlege of..."
% New activities in activities section
% Check dates on NKU scholarships
% Check all dashes
% ADD Professional organizations
% Get location of AIPS
% 
% Marsha:
% 	Place for TJ watson.  None of the others have place.
% 	Periods at end of phrase entries?
% 
% 
% Info per Company:
% - Company name
% - Person name
% - Company address
% - Datamining connection
% - Other connecting sentences

% I have a broad technical background ranging from theoretical to
% low-level including a bachelors in
% Mathematics with a focus in formal mathematics (algebra, real
% analysis, complexity theory, combinatorics, etc.).  I have implemented a 
% number of fairly large applications: my thesis; a handicap's
% programming/editing environment; an extensive LISP interpreter; a
% simple UNIX-like multiprocessing operating system for the 80286
% processor; a native code, optimizing compiler for a PASCAL-like
% language; and an accounting/organization package for a soccer league.
% I also have low-level coding and hardware experience that includes
% many digital and analog circuits, assembly language programming (video
% processing, games, LISP interpreter, etc.), and use of low-level APIs 
% (X-windows, DOS, UNIX, etc.).


\comment {

Intro
+  Ph.D. in artificial intelligence from University of Illinois.
+  interested in full-time employment for fall of 1997

Credentials
+  "Plausible Inference: An knowledge-intensive, inductive approach to
    domain modelling"
-  Approach to machine learning that uses rules (written) to 
-  Applied learning model to the grand challenge prob. of prot. str. prediction
-  Learning model is implemented in parallel on a 512 node CM5 supercomputer.
X  15,000 lines of C and LISP.
- appropriate for tough domains w. knoweldge

> Technical: (broad technical background)
- BS in Mathematics
- Fairly large applications: handicap, thesis editor/programming env.
- Low-level applications including: many digital and analog circuts, 
  x-windows, DOS, UNIX

> Interpersonal: Teaching/presentation. T.J. Watson

> My career objective
  - long been to do research in machine learning.
  - Through working at T.J. Watson and as a consultant on protein
  str. prediction I found my enthusiam and ability also lie in
  (1) working as a specialist within a larger group, and
  (2) synthesizing elegant, practical interfaces and designs for
  large software systems.

  Thus the ideal position would involve the research issues surrounding
  a concrete data mining application or product.  It would require me
  to provide expertise in machine 
  learning within a larger team.  This job would have the
  potential for publication, and the potential for growth toward
  technical management/software architect type position.

  A position with XXX-company provides many of these opportunities.
  ...

  


[RESEARCH|DEVELOPMENT], DATA-MINING, [CONSULTANT], [PROTEIN]



Fit  (Number of things makes good match) 
-  My consulting experience in bio is similar to the role of data mining
   consultant:
-  For two years I worked closely with a group of biologists encoding
   expertise foreign to myself into a framework foreign to them.
-  Enjoyed/excelled at: selling model \& arriving at common understanding.


Communicate Skills:  
   Technical, Designing, Programming, 
   Interpersonal: presentation(selling), communication, writing, management
   Eager/hard-working
}

\comment{ UNUSED STUFF


\begin{tabbing}
\hspace*{5in}\=\kill\\
\>Daniel Oblinger\\
% \>Beckman Institute\\
% \>University of Illinois\\
\>405 N. Mathews\\
\>Urbana, IL 61801\\
\>April 25, 1997
\end{tabbing}

XXX Company \\
XXX Street \\
XXX City, State \\
\vspace{.25in}

Dear XXXX recruiting,



\begin{tabbing}
\hspace*{5in}\=\kill\\
\vspace*{.5in}
\>Sincerely,\\
\vspace*{.75in}
\>Daniel A. Oblinger\\
\end{tabbing}

}


% \pagenumbering{none}
% Regular page size
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}  % was 9
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{0.2in}
\setlength{\itemindent}{.25in}

\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\topskip}{0.0in}
% \setlength{\footheight}{0.0in}
\setlength{\footskip}{0.5in}

% YAP sized pages
% \pagestyle{empty}
% \setlength{\topmargin}{-1.5in}  % .95
% \setlength{\textwidth}{5.5in}
% \setlength{\textheight}{3.7in}
% \setlength{\oddsidemargin}{-0.95in}
% \setlength{\evensidemargin}{-0.95in}

% Personal Information
\telephone{(217) 244-1503}
\email{oblinger@uiuc.edu}
\signature{Daniel A. Oblinger}


\begin{document}
\begin{letter}
 {XXX-street\\
  XXX-city-state\\
  April 25, 1997\\}

\opening{Dear XXXX Recruiter,}

I am a graduating Ph.D. from the University of Illinois in Artificial
Intelligence.  I am interested in employment at XXX, and will be 
available for full-time employment October 1997.  I will be making an
employment decision in the first half of this comming summer.

\par

Through my graduate studies I have gained considerable experience in
data-mining and its application to important/practical learning tasks.
%
My dissertation, ``Plausible Inference: A knowledge-intensive approach
to domain modeling,''  was carried out under the direction of Gerald
DeJong.
%
Plausible Inference (PI) is framework for inductive learning that
relies on several forms of structured knowledge that we have found to be
commonly available sources of domain expertise.
%
PI employs this domain expertise as a strong, problem-specific,
bias through which it is capable of inducing predictive models of
complex domains.
%
We have applied PI to a difficult biological domain: protein structure
prediction.
%
For this task we implemented a parallel version of PI in a combination
of C and LISP which ran on a CM5 supercomputer.
%
This experience serves as a strong foundation for further work bridging
reseach and development; in particular for applying learning/mining techniques
to other areas.

\par

I have participated on both academic and professional projects in a
variety of capacities.
%
The application of machine learning to the problem protein structure
prediction required me to act as an AI consultant with 
to a group of biologists.
%
We encoded their intuitions about atomic interactions as testable,
computational models of protein folding.
%
I successfully wrote papers and grant proposals with a number of
professors at the University of Illinois.
%
At T.J. Watson Research I worked with a second-line manager on the
design of an expert system shell; as part of my duties I presented
initial versions of this design to managers of those groups that would
implement the shell.
%
At Ohio State I enjoyed teaching several, and designing one,
university-level course.
%
This body of experience affords me the written, oral, interpersonal,
and organizational skills essential for continued personal growth and
far reaching contributions at XXX.


\par

My career objective has long been to do reseach and development in
machine learning.  Through past experience including T.J. Watson
Reserach and as a 
consultant on protein structure prediction I found my enthusiam and
ability also lie in (1) working as a specialist within a larger group,
and (2) synthesizing elegant, practical interfaces and designs for
large software systems.
%
Thus, the ideal position would involve both the research and
development issues surrounding a concrete data-mining/machine learning
application.  It would draw on my expertise in data mining and
software development within a larger team.  This would also have
potential for publication, and potential for growth towards a technical
management/software architect type position.

\par

A position with XXX-company affords many of these opportunities.
Your work on ...

\closing{Sincerely,}

I have a broad technical background ranging from theoretical 
(bachelors in mathematics) to low-level (wiring digital circuits).

\end{letter}

\end{document}
